Manuscript draft

### 2019-07-10 manuscript/manuscript draft.Rmd
updated manuscript draft

| Variable | Latitude | Mean annual temperature | Temperature seasonality | Potential evapotranspiration |
|----------|----------|----------|----------|----------|
| R~auto~ | 0.64 | 0.60 | 0.54 | 0.63 |
| GPP | 0.66 | 0.59 | 0.75 | 0.40 |
| NPP | 0.51 | 0.50 | 0.52 | 0.34 |
| ANPP | 0.50 | 0.38 | 0.47 | 0.32 |
| ANPP~foliage~ | 0.55 | 0.60 | 0.54 | 0.40 |
| ANPP~woodystem~ | 0.25 | 0.22 | 0.20 | 0.26 |
| BNPP~root~ | 0.31 | 0.32 | 0.31 | 0.32 |
| BNPP~rootfine~ | 0.14 | 0.16 | 0.16 | 0.11 |
| R~root~ | 0.25 | 0.16 | 0.29 | 0.04* |

@@

>>>>

| Variable | Latitude | Mean annual temperature | Temperature seasonality | Potential evapotranspiration |
|----------|----------|----------|----------|----------|
| R~auto~ | 0.64 | 0.83 | 0.54 | 0.63 |
| GPP | 0.66 | 0.61 | 0.75 | 0.40 |
| NPP | 0.51 | 0.49 | 0.52 | 0.34 |
| ANPP | 0.50 | 0.45 | 0.47 | 0.32 |
| ANPP~foliage~ | 0.55 | 0.63 | 0.54 | 0.40 |
| ANPP~woodystem~ | 0.25 | 0.23 | 0.20 | 0.26 |
| BNPP~root~ | 0.31 | 0.26 | 0.31 | 0.32 |
| BNPP~rootfine~ | 0.14 | 0.11 | 0.16 | 0.11 |
| R~root~ | 0.25 | 0.21 | 0.29 | 0.04* |

@@

R-squared values are generally highest in the major fluxes, and decrease in subsidiary fluxes. Of the major fluxes, R~auto~ and GPP are the most strongly explained by latitude and climate. Mean annual temperature explains 83% of variation in R~auto~, while temperature seasonality explains 75% of variation in GPP. The proportion of variation explained by climate and latitude decreases in NPP and ANPP. The climatic variables with the strongest explanatory power explain around 50% of the variation in these fluxes. Of the major fluxes, BNPP~root~ is the least well explained by climate and latitude, with climate explaining at most 32% of variation.

With the exception of ANPP~foliage~, the proportion of variation explained by climate and latitude in subsidiary fluxes is much lower. Climate explains at most 26% of variation in ANPP~woodystem~, 17% in BNPP~rootfine~, and 32% in R~root~. In contrast, climate strongly explains variation in ANPP~foliage~, with mean annual temperature explaining 63% of variation.
